Layered Formal Verification of an Industrial TCP/IP Stack

### 2021-05-21 SecDev21/paper.tex

\title{Verification of a TCP/IP stack}

@@

In this paper, we take a practical approach, where the security of an existing TCP/IP stack implementation written in ANSI C programming language is incrementally enhanced by replacing parts of its code with formally verified code in SPARK \cite{mccormick_chapin_2015}. SPARK 2014 is a programming language designed as a subset of the Ada language to produce highly reliable software through formal verification. For this work, the CycloneTCP, a professional-grade embedded TCP/IP library developed by the Oryx Embedded company \cite{CycloneTCP}. \Cref{Fig:TcpStack} shows the protocols supported by the library. This work focuses on the TCP and socket components of the stack. The library's TCP implementation is meant to conform with the RFC 793 protocol specifications \cite{rfc793}. The quality of the CycloneTCP is acknowledged by the AMNESIA:33 report \cite{AMNESIA33}, which classifies it as one of the most resilient TCP/IP stack. By using as a starting point such a well-tested and widely used TCP/IP implementation, the IoT industry can have an immediate benefit by adopting this work's security-enhanced version of the CycloneTCP library. 
\todo[inline]{KG:pending contributions list and fixing the next paragraph. Will be fixed when the rest of the paper is finalized.}
We present the TCP protocol in section~\ref{sec:TCP} and then briefly the
chosen stack, the Oryx Embedded one, in section~\ref{sec:stack}
before presenting the specification techniques used in section~\ref{sec:spec}
and then in sections~\ref{sec:verif} and~\ref{sec:API} we explain how we
formally implemented in SPARK the TCP user functions and how we hardened the
user's API. Finally we end in section~\ref{sec:results} by showing the results
of our work.

@@

The reader can refer to the code at \url{https://github.com/AdaCore/Http_Cyclone}.

>>>>

\title{Layered Formal Verification of an Industrial TCP/IP Stack}

@@

In this paper, we take a practical approach, where the security of an existing TCP/IP stack implementation written in ANSI C programming language is incrementally enhanced by replacing parts of its code with formally verified code in SPARK \cite{mccormick_chapin_2015}. SPARK 2014 is a programming language designed as a subset of the Ada language to produce highly reliable software through formal verification. For this work, the CycloneTCP, a professional-grade embedded TCP/IP library developed by the Oryx Embedded company \cite{CycloneTCP}. \Cref{Fig:TcpStack} shows the protocols supported by the library. This work focuses on the TCP and socket components of the stack. The library's TCP implementation is meant to conform with the RFC 793 protocol specifications \cite{rfc793}. The quality of the CycloneTCP is acknowledged by the AMNESIA:33 report \cite{AMNESIA33}, which classifies it as one of the most resilient TCP/IP stack. By using as a starting point such a well-tested and widely used TCP/IP implementation, the IoT industry can have an immediate benefit by adopting this work's security-enhanced version of the CycloneTCP library.

\todo[inline]{KG:pending contributions list and fixing the next paragraph. Will be fixed when the rest of the paper is finalized.}

We present the TCP protocol in section~\ref{sec:TCP} and then briefly the
chosen stack, the Oryx Embedded one, in section~\ref{sec:stack}
before presenting the specification techniques used in section~\ref{sec:spec}
and then in sections~\ref{sec:verif} and~\ref{sec:API} we explain how we
formally implemented in SPARK the TCP user functions and how we hardened the
user's API. Finally we end in section~\ref{sec:results} by showing the results
of our work.

@@

% The reader can refer to the code at \url{https://github.com/AdaCore/Http_Cyclone}.
